\documentclass[11pt]{scrartcl}
\usepackage{dominatrix}
\usepackage{solarized-light}
\lstset{
language=python
}

\renewcommand\thesection{Problem \arabic{section}}
\renewcommand\thesubsection{\arabic{section} (\alph{subsection})}
\renewcommand\thesubsubsection{(\roman{subsubsection})}
\DeclareMathOperator{\AU}{AU}
\DeclareMathOperator{\arcsec}{arcsec}
\DeclareMathOperator{\pc}{pc}
\DeclareMathOperator{\km}{km}
\DeclareMathOperator{\m}{m}
\DeclareMathOperator{\cm}{cm}
\DeclareMathOperator{\rad}{rad}
\DeclareMathOperator{\s}{s}
\DeclareMathOperator{\degrees}{degrees}
\DeclareMathOperator{\degree}{degree}
\DeclareMathOperator{\arcmin}{arcmin}
\DeclareMathOperator{\parsec}{parsec}
\DeclareMathOperator{\lightyears}{light-years}

\newcommand\pow[2]{\ensuremath{#1 \times 10^{#2}}}

\title{Problem Set 2}
\subject{ASTR 1404 Stars, Galaxies, and Cosmology}
%\author{James H. Applgate}
\begin{document}
\maketitle

\section{}

A visual binary has a parallax of $0.1\arcsec$, a separation of $4 \arcsec$, and an orbital period of 100 years. Star B is $3 \arcsec$ from the Center of Mass (CM) and Star A is $1 \arcsec$ from the CM.

\subsection{}

What is the distance to the binary?

\subsection{}

What is the physical distance between the two stars?

\subsection{}

What is the total mass of the binary?

\subsection{}

What are the masses of each of the two stars?


\section{}

The bright star of $\alpha$Centauri is actually a binary. The parallax of $\alpha$Cen is $0.752\arcsec$, the orbital period is 80.1 years, and the separation between $\alpha$CenA and $\alpha$CenB is $17.6\arcsec$.

\subsection{}

What is the distance to $\alpha$Cen?

\subsection{}

What is the physical separation between the stars?

\subsection{}

What is the total mass?

\subsection{}

$\alpha$CenA is $7.9\arcsec$ from the CM and $\alpha$CenB is $9.7 \arcsec$ from the CM. What are the masses of each star?


\section{}

The bright star Procyon is a binary. The parallax of Procyon is $0.29\arcsec$, the separation between star A and star B is $4.5 \arcsec$, and the orbital period is 40.6 years.

\subsection{}

What is the distance to Procyon?

\subsection{}

What is the physical separation between the stars?

\subsection{}

What is the total mass of the binary?

\subsection{}

What are the masses of each of the two stars? $\theta_A = 1.2\arcsec$ and $\theta_B = 3.3\arcsec$.

\end{document}
